Run the model

### 2019-05-28 docs/slides/GainesLab_presentation.Rmd
Added slides for gaines lab and new manuscript by John

---
title: "Marine Conservation and Fishing Effort Markets[^*]"
author:
  - Villaseñor-Derbez J.C.$^1$
  - Lynham J.$^2$
  - Costello C.$^{1, 3}$
institute: 
   - $^1$Bren School, UCSB
   - $^2$Department of Economics, UHM
   - $^3$emLAB, UCSB
subtitle: "NCEAS-Future Earth Working Group"
date: "May 6, 2019"
output: 
  beamer_presentation: 
    theme: Darmstadt
header-includes:
  - \usepackage{media9}
  - \usepackage{eso-pic,graphicx,transparent}
---

[^*]: This is work in progress developed for the NCEAS working group. Please do not share externally. Results are yet to be refined and peer-reviewed.

\AddToShipoutPictureFG{
  \AtPageCenter{% or \AtTextCenter
    \makebox[0pt]{\rotatebox[origin=c]{45}{%
      \scalebox{5}{\texttransparent{0.3}{DRAFT}}%
    }}
  }
}

@@

@@

- Generalizability to Palau

@@

@@

### Effort displacement by large-scale MPAs

- Does effort displacement imply revenue losses from VDS?

- Does a 30\% closure mean a 30\% loss in revenue?

@@

@@

  - Can these costs be reduced or eliminated?

@@

  - Where do they go?

@@

$$\Pi_i(E_i,X_i,R) = pqE_iX_i\Omega_i-cE_i^\beta$$

@@

# Generalizability to Palau

## Palau Vessel-day schemes

  - Tradable

- Under no trading, implementing a reserve is costly

  - More fish movement reduces costs

- Trading lessens the blow of a spatial closure

  - \% costs avoided by trading decrease as biomass in implementing patch increases

- Allocation rules matter

  - A biomass-based allocation ($\alpha = 0$) reduces long-term costs

@@

## Displaced vessels

```{r}
knitr::include_graphics(here("docs", "img", "fishing_raster_displaced.png"))
```

## Non-displaced vessels

```{r}
knitr::include_graphics(here("docs", "img", "fishing_raster_not_displaced.png"))
```

## Difference

```{r}
knitr::include_graphics(here("docs", "img", "fishing_raster_difference_between_groups.png"))
```

# GFW Data

## Effort vs catches

```{r}
knitr::include_graphics(here("docs", "slides", "img", "catch_effort_plot.png"))
```

## Effort and revenues

```{r}
knitr::include_graphics(here("docs", "img", "revenue_FFA_GFW_linear.pdf"))
```

>>>>

---
title: "Fishery Markets and Large-Scale Marine Conservation"
author:
  - Villaseñor-Derbez J.C.
  - Lynham J.
  - Costello C.
subtitle: "Gaines Lab"
date: "May 28, 2019"
output: 
  beamer_presentation: 
    theme: Darmstadt
header-includes:
  - \usepackage{media9}
---

@@

- Model predictions

@@

- Palau National Marine Sanctuary

- Conclusions

@@

- Only 3\% of the ocean under "fully protected" MPAs

- Goals to meet 10 - 30\%

- Opportunity costs of closing areas to fishing

- How do we incentize conservation?

### Guiding question

- Will rights-based approaches to managing natural resources facilitate, or impede large-scale conservation?

- Vessel-day scheme in the PNA region may hold the answer

@@

@@

  - Does a 30\% closure mean a 30\% effort displacement and therefore a 30\% loss in revenue?

@@

  - Can these costs be reduced or eliminated by appropriately designing markets?

@@

@@

$$\Pi_i = pqE_iX_i\Omega_i-cE_i^\beta$$

@@

@@

# Palau

## Palau National Marine Monument

- Close **80\%** of its EEZ to **all** industrial fishing activities

- To be closed December 2020

- Have not evaluted the possible implications

## Likely costs to Palau

```{r, fig.widht = 4, fig.align = "left"}
knitr::include_graphics("../img/plw_2018_slides.png")
```

## Fisheries management in Palau

  - "Tradable"

### Rights-based management for conservation

Two market features can eliminate costs of conservation:

- Trading

- Biomass-based allocation

### 2019-05-28 scripts/model/2_run_model.Rmd
Added slides for gaines lab and new manuscript by John

```{r, fig.height = 3.5, fig.width = 4.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          theta = as.character(theta)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Costs\n(% of case with R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   # facet_wrap(~trade, ncol = 1) +
   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
                                  override.aes = list(size = 0.5))))
```

>>>>

```{r, fig.height = 3.5, fig.width = 4.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          theta = as.character(theta)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = alpha, group = paste(alpha, theta), linetype = theta)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Losses\n(relative to R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   # facet_wrap(~trade, ncol = 1) +
   guides(color = guide_colorbar(title = quo("Allocation\nparameter ("~alpha~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = quo("Movement\nparameter ("~theta~")"),
                                  override.aes = list(size = 0.5))))
```
